### 2016-08-30 version0.0/paper3.tex
Applying M.D.'s comments on the ch.3

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying structure of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.

@@

    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.

@@

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

>>>>

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of machine learning/data mining algorithms and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying relation of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.

@@

     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
     Users must decide the size of the network based on their data set and their usage of the results.
     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are well established. 
     In order to create maps that we can get the most information from them, we varied the initial values for the maps.
     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose a suitable size for the maps we generated, and decided that based on the size of our sample, for the 2D SOMs, $10\times10$ gives us the most information.
     Any map higher than this size, repeats the same results and become very time consuming.
     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.

@@

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown non-linear or linear correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
